AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-24 chapters/05-discussion.tex
Fix typos in 5.1

The aim of the project was to design and build a prototype of a High-Altitude
Balloon modular platform, similar in principle to buses used in the satellite
industry, and evaluate both the feasibility of such a platform and its
performance. The platform was required to allow for stable internal
communications between the payloads and the \acrlong{obc}, tracking of
ancillary data (\acrshort{gnss} co-ordinates and altitude) and reliable
transmission of the collected telemetry to one or multiple ground stations 
through a low-power radio channel. In this chapter, the \acrshort{ahabus}
platform prototype is evaluated against these aims, firs through general 
qualitative observations and analysis of the prototype's behaviour, then by
analysing the results of tests discussed in chapter \ref{ch:results}.

>>>>

The aim of the project was to design and build a prototype of a High-Altitude
Balloon modular platform, similar in principle to buses used in the satellite
industry, and evaluate both the feasibility of such a platform and its
performance. The platform was required to allow for stable internal
communications between the payloads and the \acrlong{obc}, tracking of
ancillary data (\acrshort{gnss} co-ordinates and altitude) and reliable
transmission of the collected telemetry to one or multiple ground stations 
through a low-power radio channel. In this chapter, the \acrshort{ahabus}
platform prototype is evaluated against these aims, first through general 
qualitative observations and analysis of the prototype's behaviour, then by
analysing the results of the tests discussed in chapter \ref{ch:results}.
